\documentclass{letter}
%\documentclass{article}
\usepackage[utf8]{inputenc}
% включаем переносы для русского и английского языка
\usepackage[english]{babel}
% Начинать первый параграф раздела следует с красной строки
% \usepackage{indentfirst}
% \setlength{\parindent}{5mm}
% Выбор внутренней TEX−кодировки
% \usepackage [T2A]{fontenc}

\usepackage{cmap}


\usepackage{hyperref}

\signature{Alexander Kindyakov}
\address{akindyakov@gmail.com}

\begin{document}
\begin{letter}
\newline
\opening{Dear Sir,}

I'm writing to express my interest in ... position posted on ... website.
I believe that my technical experience makes me the competitive candidate for this position.

I have a strong C++ and Python skills. I use both of it every day for 6 years in my work and in my pet--projects.

I have 3 years experience with high--performance computing.
I have written cluster computations, created production data processing on Map--Reduce system (YaMR and YT).
At this moment I'm working on the large scale document processing system that handles 10PiB of web documents in a day.
It compute wide range text features and large math computations on it.

I have 2 years of experience with distributed software.
I've worked on the distributed key--value storage ($\approx100$ servers in one cluster).
This is specific DB provided high-speed read--only data availability and fault tolerance.

I have small experience with ML frameworks and AI but I have the deepest curiosity to learn it.

I really like what you do and impressed by your progress. You made an awesome work in a short time.
It is a great pleasure and honor to be part of the team who create a humankind future.
I hope I am chosen for the position.
Looking forward to your reply.

\closing{Yours sincerely,}
\end{letter}
\end{document}
