\documentclass[a4paper, 10pt]{article}
%\documentclass{article}
\usepackage [utf8] {inputenc}
% включаем переносы для русского и английского языка
\usepackage[english,russian]{babel}
% Начинать первый параграф раздела следует с красной строки
\usepackage{indentfirst}
% Выбор внутренней TEX−кодировки
\usepackage [T2A]{fontenc}

\usepackage{cmap}
\usepackage{multirow}

\usepackage{xcolor}

\usepackage{hyperref}
\definecolor{LINKCOLOUR}{rgb}{0.1,0.0,0.9}
\hypersetup{colorlinks,breaklinks,urlcolor=LINKCOLOUR,linkcolor=LINKCOLOUR}

\usepackage{geometry} % Меняем поля страницы
\geometry{left=20mm}% левое поле
\geometry{right=15mm}% правое поле
\geometry{top=15mm}% верхнее поле
\geometry{bottom=15mm}% нижнее поле

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\raggedright}{\color{green}}{0em}{}[\titlerule] % Text formatting of sections
%\titleformat{\section}{\large\scshape\raggedright}{\color{green}}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{2pt}{3pt}{3pt} % Spacing around sections

\usepackage{longtable}
\usepackage{enumitem}

\pagestyle{empty}

\begin{document}

{\Large\textbf{Alexander Kindyakov}}

\begin{flushright}
    {\itshape
        Moscow, Russia \\
        +7--926--453--25--30 \\
        \href{mailto:akindyakov@gmail.com}{akindyakov@gmail.com} \\
        \href{https://github.com/akindyakov}{github.com/akindyakov} \\
        \href{http://ru.linkedin.com/in/alexanderkindyakov}{ru.linkedin.com/in/alexanderkindyakov} \\
    }
\end{flushright}


\section{Experience}
\begin{longtable}{p{20mm}|p{140mm}}
2013 ---
& \textbf{``Yandex''} \\
& \href{https://yandex.ru/}{yandex.ru} \\
& Software Engineer \\
& \begin{itemize}[topsep = 0pt, itemsep = 0pt]
    \item[$\dashv$] Web--Search antispam.
    \item[$\dashv$] Distributed in--memory data storage (cluster size 50--100 nodes):
        \begin{itemize}[topsep = 0pt, itemsep = 0pt]
            \item revised response formats;
            \item solved exception--safety problem for master server;
            \item solved replicas synchronization problem;
            \item built generating data sets for different entities of this storage;
            \item made monitorings for all activity on the cluster.
        \end{itemize}
    \item[$\dashv$] High--performance web--documents processing system:
        \begin{itemize}[topsep = 0pt, itemsep = 0pt]
            \item made code refactoring (optimization, decomposition, design correction);
            \item created monitorings for key point of the workflow;
            \item moved all computations from cluster (size 70--90 nodes) solution to Map--Reduce system;
            \item substituted code solution for serializing compiled byte--code;
            \item implemented new features like using Vowpal Wabbit and MatrixNet;
            \item created service for an online document processing instead of slow offline batch process.
        \end{itemize}
\end{itemize}
\\

2011 --- 2013 & \textbf{``3Detection Labs''} \\
& \href{http://www.3detection.com/}{www.3detection.com} \\
& Software Engineer \\
& \begin{itemize}[topsep = 0pt, itemsep = 0pt]
    \item[$\dashv$] Automatic control system for robotic 3--degree--of--freedom manipulator.
    \item[$\dashv$] Testing, installation and problem diagnostics software for robotic arm.
    \item[$\dashv$] Robot navigation system based on the telemetry, GPS and Earth magnetic field.
    \item[$\dashv$] Remote control and adjustment system for mobile robot.
    \item[$\dashv$] Image recognition for mobile robot computer vision.
    \item[$\dashv$] AI for mobile robot (project was scrapped).
\end{itemize}
\\
\end{longtable}

\section{Education}
\begin{longtable}{p{20mm}|p{140mm}}
2008 --- 2014
& ``BMSTU'' \\
& \href{http://www.bmstu.ru}{www.bmstu.ru} \\
& Mechatronics, Robotics, and Automation Engineering \\
& Master's degree \\
& Diploma with honours \\
& Graduation project: ``\textit{Precise drive for space satellite robot arm}'' \\
& Research advisor: Boshlyakov Andrey \\
\end{longtable}

%\section{Language proficiency}
%\begin{longtable}{p{20mm}|p{140mm}}
%& \begin{itemize}[topsep = 0pt, itemsep = 0pt]
%    \item[+] Russian --- native
%    \item[+] English --- intermediate
%\end{itemize} \\
%\end{longtable}

\end{document}

